The \frb\ Observing Campaign: Multi-Telescope Radio Burst and Implications for the FRB Population

### 2016-12-19 repeater-vladata.tex
repetition disc. flux disn disc

 \caption{Dynamic spectra (time vs frequency intensity maps) for the nine VLA bursts. Starting at the top left, they correspond to bursts 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649. Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
 \label{fig:sgram}}
\end{center}
\end{figure*}

@@

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.3\columnwidth]{spec_57646.png}
  \includegraphics[width=0.3\columnwidth]{spec_57648.png}
  \includegraphics[width=0.3\columnwidth]{spec_57649.png}
 \end{minipage}
\caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz. Orthongonal circular polarizations (RR and LL) are plotted separately. **LABELS ALL SAME FREQ. SOME SHOULD START HIGHER FOR DROPPED CHANNELS**
\label{fig:spec}}
\end{center}
\end{figure*}

@@

\subsection{Temporal Statistics}
Burst detections were made very inhomogenously through the larger (63 hours) observing campaign of FRB 121102. In the first 30 hours of observing at S-band no bursts were detected, while nine bursts were detected in the last 27 hours of S-band observing. The data quality is high, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary. Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$ hour$^{-1}$ (95\% confidence limit). The mean detection rate for the last part of the campaign was $\rm{R}=0.3$ hour$^{-1}$.

@@

\subsection{FRB Flux Distribution}
Doubts were cast on the first FRB detection (``Lorimer burst'') due to its unusually high brightness. The lack of lower-significance detections suggested that this burst was unlikely to be part of any astrophysical population. With more detections, it has become clear that the FRB population has a relatively flat flux distribution \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}. This fact was demonstrated with yet another detection of an extremely bright FRB \citep{2016arXiv161105758R}.

Flux distribution... (\S \ref{sec:disn})
Scaling up assumes that this source is representative. Propagation effects may amplify or alter burst brightness statistical properties. Some such effects are possible near the burst source (e.g., Jim's caustic analysis), which would effectively be intrinsid in this context.

\subsection{Repetition}
Discussion of ``red spectrum'' and \citet{2016MNRAS.458L..89C}. Bursts predict bursts therefore repetition constraints of other FRBs are likely weaker than claimed...

Constraints on repetition assuming "red spectrum" for whole population. Simulation using observed burst temporal statistics...

Intrinsic versus refractive scintillation...

Fewer FRBs out there...

>>>>

 \caption{Dynamic spectra (time vs frequency intensity maps) for the nine VLA bursts. Starting at the top left, they correspond to bursts 57623, 57633.68, 57633.70, 57638, 57643, (bottom left) 57645, 57646, 57648, and 57649. Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
 \label{fig:sgram}}
\end{center}
\end{figure*}

@@

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.3\columnwidth]{spec_57646.png}
  \includegraphics[width=0.3\columnwidth]{spec_57648.png}
  \includegraphics[width=0.3\columnwidth]{spec_57649.png}
 \end{minipage}
\caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz. Orthongonal circular polarizations (RR and LL) are plotted separately and example errorbars are shown at the top right of each panel. A binned spectrum is overplotted with a solid line.
\label{fig:spec}}
\end{center}
\end{figure*}

@@

\subsection{Temporal Statistics}
\label{sec:temp}
Burst detections were made very inhomogenously through the larger (63 hours) observing campaign of FRB 121102. In the first 30 hours of observing at S-band no bursts were detected, while nine bursts were detected in the last 27 hours of S-band observing. The data quality is high, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary. Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$ hour$^{-1}$ (95\% confidence limit). The mean detection rate for the last part of the campaign was $\rm{R}=0.3$ hour$^{-1}$.

@@

\subsection{FRB Flux Distribution}
Doubts were cast on the first FRB detection (``Lorimer burst'') due to its unusually high brightness. The lack of lower-significance detections suggested that this burst was unlikely to be part of any astrophysical population. With more detections, it has become clear that the FRB population has a relatively flat flux distribution \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}. This fact was recently demonstrated by yet another detection of an extremely bright FRB \citep{2016arXiv161105758R}.

**Discussion of luminosity/flux distribution analysis presented in \S \ref{sec:disn})**

It is not yet clear whether \frb\ can be treated as a representative of the broader FRB population. \citet{2016Natur.531..202S} describes burst spectral structure that is intrinsic, or at least dominated by propagation effects close to the emitting region. On the other hand, \citep{CORDES} have identified a variety of propagation effects in our own Galaxy that can plausibly modify the observed brightness distribution.

\subsection{Repetition}
The burst rate analysis presented in \S \ref{sec:temp} shows that the detection probability of \frb\ is not stationary. As mentioned above, this could be caused by intrinsic events (e.g., magnetar outburst) or propagation effects. In either case, it demonstrates that \frb\ has a kind of "red spectrum" temporally, in which bursts tend to cluster in time \citep{2016MNRAS.458L..89C}. The detection of a burst improves odds of finding more bursts in near-future observations.

If this statistical property describes other FRBs, it weakens previous constraints on repetition \citep{2015MNRAS.454..457P,2015ApJ...807...16L}. It is possible that other FRBs have repeating bursts, although calculating a limit requires knowing the temporal powerlaw that defines the repetition. Observations of \frb\ have not yet detected enough bursts to reliably measure that index. This repetition also implies that there are fewer phyiscal sources of FRBs than implied by the burst detection rate.
